---
title: Longitudinal Association of Video Gaming With Severe Behavior Problems Among Youth
authors:
  - name: Bader Chaarani
    department: Department of Psychiatry
    affiliation: University of Vermont
    location: Burlington, VT 05405
    email: melmarsr@uvm.edu
  - name: Samuel W. Hawes
    department: Psychology
    affiliation: Florida International University
    location: Miami, FL
    email: shawes@fiu.edu
  - name: Raul Gonzalez
    department: Psychology
    affiliation: Florida International University
    location: Miami, FL
    email: gonzara@fiu.edu

abstract: |
 Et nec sed eleifend quam in tincidunt, sodales. Litora tristique ac lacinia veleu et molestie. Iaculis vestibulum erat iaculis urna tellus urna quis quis quis. Primis curae dolor ut aptent. **Objective**  dis tortor quisque auctor pellentesque sed ideros lacus laoreet id nibh. Ut varius donec justo est aenean auctor. At, lacusfinibus tempor inceptos! Nisi in a est semper vel velit consequat. **Methods.** Ultrices acmetus a egestas curabitur, enim feugiat ornare. Diam tincidunt natoque tinciduntnisl potenti class. Feugiat vivamus sagittis, cras. Nibh, dis litora amet. Sednibh, turpis, a tempor, id maximus libero id feugiat ut fermentum vulputate. **Results.**  Cursus euismod facilisis sed sapien aenean facilisis proin tincidunt. Feugiateget, mus neque eu integer curabitur pulvinar. At, mattis dignissim sed vehiculaornare hac tortor et, sem. **Conclusions.** Nec ornare venenatis est primis curae dolor ut aptent dis tortor quisque auctor pellentesque. Sed ideros lacus laoreet id nibh. Ut varius donec justo est aenean auctor. Et nec sed eleifend quam in tincidunt, sodales. Litora tristique ac lacinia veleu et molestie.

    keywords:
    *video games*,
    *behavior problems*,
    *longitudinal analyses*

header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
   - \usepackage{threeparttable}
   - \usepackage{setspace}
   #- \usepackage{leading}
   #- \leading{15pt}
   #- \singlespacing
mainfont: arial
sansfont: arial
monofont: arial
fontsize: 15pt
indent: true
output: 
  rticles::arxiv_article

bibliography: "references.bib" #references.bib
biblio-style: unsrt

---

# "windsorize" Weekly_Gaming_Hours_T2 at <=28?

```{r config}
#| include: FALSE
#| echo: FALSE

knitr::opts_chunk$set(echo = T, message=F, warning=F, error=F, 
                      comment=NA, cache=T, code_folding=T,
                      R.options=list(width=220), fig.align='center', 
                      out.width='75%', fig.asp=.75, dev="cairo_pdf")

```

```{r}
#| include: FALSE
#| results: FALSE
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

setwd("/Users/shawes/Library/CloudStorage/GoogleDrive-swh004@gmail.com/My Drive/Projects/gaming_behav/main")
library(lme4)
library(lmerTest)
library(tidyverse)
library(arrow)
library(afex)
library(formatR)
library(report)
library(easystats)
library(parameters)
library(modelbased)
library(effectsize)
library(see)
library(performance)
library(insight)
library(DT)
library(data.table)
library(arsenal)
library(kableExtra)
library(equatiomatic)
library(gtsummary)
library(ggstatsplot)
library(papaja)
library(stringi)
library(lavaan)
library(corrr)

df_long<- read_csv("/Users/shawes/Library/CloudStorage/GoogleDrive-swh004@gmail.com/My Drive/Projects/gaming_behav/main/_data/df_long.csv")
```

&nbsp;         <!-- Option #1 -->
&nbsp;

# Introduction
There has been much debate and research on the relationship between violent video games and aggressive behavior problems among youth. Some studies have found that playing violent video games may be associated with increased aggressive thoughts, emotions, and behaviors. However, other research has found no such relationship, or that the relationship is small and may not be significant. It is important to note that aggression is a complex behavior that is influenced by many factors, including genetics, social environment, and individual experiences. There is no single cause of aggression, and it is likely that the relationship between violent video games and aggressive behavior is complex and multifaceted (GP). 

It is also important to consider that not all youth who play violent video games will exhibit aggressive behavior, and not all youth who exhibit aggressive behavior have played violent video games. It is possible that other factors, such as a history of exposure to violence, family or social problems, or individual psychological or psychiatric conditions, may contribute more significantly to aggressive behavior problems. Overall, it is important to consider the potential impact of violent video games on youth, as well as the many other factors that may influence aggressive behavior. However, more research is needed to fully understand the relationship between violent video games and aggressive behavior problems among youth (GP).

# Methods
\label{sec:headings}

## Sample
The ABCD sample was largely recruited through public, private, and charter elementary schools. The ABCD study adopted a population neuroscience approach to recruitment [@falk2013; @paus2013] by using epidemiologically informed procedures to ensure demographic variation in its sample that would mirror the variation in the US population of 9- and 10-year-olds [@garavan2018]. A probability sampling of schools was conducted within the defined catchment areas of the study’s nationally distributed set of 21 recruitment sites in the US. All children in each sampled school were invited to participate after classroom-based presentations, distribution of study materials, and telephone screening for eligibility. Exclusions included common MRI contraindications (such as cardiac pacemakers and defibrillators, internal pacing wires, cochlear and metallic implants, and Swan-Ganz catheters), inability to understand or speak English fluently, uncorrected vision, hearing or sensorimotor impairments, history of major neurologic disorders, gestational age less than 28 weeks, birth weight less than 1200 g, birth complications that resulted in hospitalization for more than 1 month, current diagnosis of schizophrenia, moderate or severe autism spectrum disorder, history of traumatic brain injury, or unwillingness to complete assessments. The ABCD study sample also includes 2105 monozygotic and dizygotic twins. The ABCD study’s anonymized data, including all assessment domains, are released annually to the research community. Data on race and ethnicity are not included in the ABCD study data. Information on how to access ABCD study data through the National Institute of Mental Health Data Archive is available on the ABCD study
data-sharing webpage.

Participants were enrolled in the ongoing, longitudinal ABCD Study, and the study data were from the annual 4.0 data release (https://data-archive.nimh.nih.gov/abcd). The ABCD Study recruited 11,874 healthy children, ages 9–10, to be followed into early adulthood. Participants across 21 study sites were recruited through public and private elementary schools, with sampling approaches intended to yield a final sample that approximated national sociodemographic characteristics. The ABCD study was approved by the appropriate institutional review boards: most ABCD research sites rely on a central Institutional Review Board at the University of California, San Diego for the ethical review and approval of the research protocol, with a few sites obtaining local IRB approval. Participants provided written assent, and their legal guardians written consent, for participation.

## Measures
### Screen Time Survey
Participants were administered a screen time survey that asked how much time they spend engaged in different types of screen time on a typical weekday and a typical weekend day. The different screen time categories were as follows: “Watch TV shows or movies?”; “Watch videos (such as YouTube)?”; “Play video games on a computer, console, phone, or other device (Xbox, Play Station, iPad)?”; “Text on a cell phone, tablet, or computer (eg, GChat, Whatsapp, etc.)?”; “Visit social networking sites like Facebook, Twitter, Instagram, etc?”; and “Video chat (Skype, Facetime, etc)?” For each of these activities, the participants responded with how much time they spent per day doing them. They could answer none, less than 30 minutes, 30 minutes, 1 hour, 2 hours, 3 hours, or 4 hours. Answers were mostly none for the texting, social networking, and video chatting categories, as expected for this age range. For each participant, a total weekly video-gaming score was derived as the sum of (video-gaming hours per weekday × 5) + (video-gaming hours per weekend day × 2). Using the video-gaming score, we defined a group of NVGs who never played video games (0 gaming hours per week) and a group of VGs who played 3 hours per day (21 hours per week) or more. This threshold was selected because it exceeds the American Academy of Pediatrics screen time guidelines [@2022z], which recommends that video-gaming time be limited to 1 to 2 hours per day for older children.

### Severe Behavior Problems
Mental health symptoms were evaluated using the Child Behavior Checklist (CBCL) [@achenbach2000] and the Schedule for Affective Disorders and Schizophrenia for School-Age Children–Present and Lifetime version for DSM-5 (K-SADS-PL) [@kaufman1997; @kobak2013]. Raw scores of behavioral (externalizing, aggression, oppositional-defiant problems, conduct problems) and psychiatric categories (Diagnostic and Statistical Manual of Mental Disorders, Fifth Edition diagnoses of depression oppositional-defiant disorder, and conduct disorder) were obtained via parent-report of the self-administered computerized version of each of these measures.

### Callous-unemotional traits
We classified callous-unemotional traits using a four-item measure derived and validated in previous studies using data from the ABCD Study [@hawes2021; @waller2020] that included one item from the CBCL–Parent Report (“lack of guilt after misbehaving”) and three (reverse-scored) items from the Strengths and Difficulties Questionnaire–Parent Report [@goodman1997] (e.g., “is helpful if someone is hurt or upset”). This measure showed strong psychometric properties, including discrimi- nant (e.g., crossover suppression effect between callous-unemotional traits and anxiety) and convergent validity, measurement invariance, independent replication, and overlap with other commonly used measures of callous-unemotional traits [@hawes2020c]. Finally, we also derived maximum a posteriori scale scores that provided person-specific callous-unemotional trait factor scores.

### Group classification
To attain a robust sample size to explore DBD groups, we inclusively classified the presence of DBDs on the basis of youths scoring at or above the borderline clinical range (i.e., T-scores > 67) on either the CBCL DSM- oriented conduct problems subscale or oppositional defiant problems subscale or receiving a K-SADS-PL conduct disorder or oppositional defiant disorder diagnosis (N=995) [@hawes2021; @byrd2021]. Youths with DBDs were further categorized on the basis of extremes of callous-unemotional traits. The DBD+CU group had high callous-unemotional traits based on a conjunction of summed scores >4 on the summed callous-unemotional traits measure and callous-unemotional maximum a posteriori scores in the 90th percentile (DBD+CU traits, N=198). To maximize phenotypic differences between groups, youths in the DBD-only group had summed scores of zero on the callous-unemotional traits measure (N=276).

### Potential confounders 
To account for the potentially confounding effects of attentional, cognitive, or emotional dif- ficulties that are often comorbid with DBDs, all analyses included CBCL DSM-oriented attention problems and in- ternalizing subscale scores as covariates. We also covaried for sex, age, race/ethnicity, and parental education.

### Participant Inclusion Criteria
Participants were included if they had (1) xxxxx, (2) xxxxx, and (3) had complete information on the screen time survey and for all other variables (CBCL, age, sex, and parental income).

### Demographic Characteristics and Mental Health Measures
The child’s age and sex were reported by the parent at the baseline assessment. A trained researcher measured children’s height (to the nearest inch) and weight (to the nearest 0.1 lb). Height and weight were assessed 2 times, and means were recorded. Height and weight were converted to body mass index (BMI) age-, sex-, weight-, and height-specific z scores (according to the Centers for Disease Control and Prevention age-, sex-, height-, and weight-specific BMI cutoffs [@kuczmarski2002]). IQ scores were derived from the National Institutes of Health Toolbox cognition battery [@zelazo2013] as the mean of crystalized intelligence and fluid intelligence composite, age-corrected scores. Demographic characteristics were compared between VGs and NVGs using a 2-tailed t test except for sex, which was compared using a x2 test (Table 1). 

## Analytic Strategy
Analysis of variance and x2 tests were used to compare the demographic characteristics between NVGs and VGs. The Permutation Analysis of Linear Models (PALM) general linear model26 was used to run vertexwise permutation analyses comparing cortical task-specific BOLD signal between NGVs and VGs for correct stop vs correct go and incorrect stop vs correct go conditions of the SST, as well as 0-back vs fixation and 2-back vs fixation conditions of the n-back test, with age (months), sex, scanner serial number, IQ, puberty, and combined parental income included as nuisance covariates. The analyses accommodated the nonindependence of the participants by incorporating information on sibling status as a nested covariate in the model using PALM’s exchangeability blocks,27 which restrict the shuffling to only occur among the observations that share the same family index, that is, within-block only. In addition, performance measures, including SSRT and correct go RT in the SST as well as D and correct RT in the n-back, were compared between NVGs and VGs using analysis of covariance (with the same covariates as those included in neuroimaging analyses). All statistical tests were 2-sided. False discovery rate–corrected P values and statistical maps were considered significant at P < .05.

We used multinomial logistic regression to examine differences in reward-related brain activation in regions of interest between the following groups: youths with DBDs compared with typically developing youths, youths with DBD only compared with typically developing youths, youths with DBD+CU compared with typically developing youths, and youths with DBD only compared with youths with DBD+CU. We also examined whether sex moderated these associations. Next, we used latent variable modeling to determine whether the spatial pattern of coactivation across all 16 reward- relevant regions (i.e., relative contribution of each region to a broader reward network) differed between groups during reward anticipation and receipt. We specified a second-order factor model in which each (separably lateralized) region of interest loaded onto a right or left reward factor. These first- order right and left lateralized factors were then used as indicators of a higher-order factor, representing an over- arching latent reward network factor (Figure 2). The re- siduals of homologous region-of-interest pairs were specified to correlate (e.g., the left OFC with the right OFC).

The reward network factor model allowed us to examine group differences in activation at a network level, supple- menting the region-of-interest analyses in several ways. First, we could evaluate how each region contributed to the hy- pothesized reward network and assess whether the network could be modeled similarly across groups. We used mea- surement invariance testing (via the DIFFTEST procedure in Mplus, version 7 [32]) to evaluate the reward network factor model across groups (i.e., configural invariance) and whether each region contributed to the higher-order network equivalently across groups (i.e., metric and scalar invariance) (see the Methods section in the online supplement). Second, our modeling approach allowed us to test for group differ- ences in mean levels of activation at the network level (i.e., not just individual regions), which was made more advantageous given that latent variables are modeled free of measurement error, resulting in increased statistical power.

All analyses were conducted using Mplus, version 7 (32), with models specified using maximum likelihood estimation with robust standard errors and a Monte Carlo numerical integration algorithm. Complex sampling and recruitment procedures for the ABCD Study were accounted for using cluster correction (i.e., for sibling pairs) and stratification sampling (i.e. study site) procedures (32). The median absolute deviation was used to identify study outliers, with values winsorized at 62.5 times the median absolute deviation. Outlier cases did not exceed 5% for any region.

### Structural Equation Modeling
To address any confounding effects of time spent watching videos, behavioral problems, or psychiatric disorders on BOLD changes associated with video gaming, we used structural equation modeling to model the association between video gaming and activation in the n-back task and SST, with video watching, behavioral problems, and psychiatric disorders scores included as covariates (Figure 1). B Coefficients from the fMRI general linear model (model described in the eMethods in the Supplement) were extracted using MATLAB (MathWorks) for each task and contrast from vertexes showing significant differences between NVGs and VGs in the vertexwise analyses. Mean B coefficients were computed for each contrast and included as the BOLD signal variable in the model. Total behavioral problems and psychiatric disorder scores were calculated from the CBCL20 as the sum of the scores of all of the problem and psychiatric items, respectively. The model was specified in R software, version 4.0.4 (R Foundation for Statistical Computing) using the structural equation.

## Results
```{r descriptives}
#| results: "asis"
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

## Create a (grouped) descriptives table 
descriptives  <- tableby.control(test=FALSE, total=TRUE, cat.simplify=TRUE,
                               numeric.test="kwt", cat.test="chisq",
                               numeric.stats=c("N", "meansd", "median", "range" 
                                               ), #"Nmiss2"
                               cat.stats=c("countpct"), #"Nmiss2"
                               stats.labels=list(N='Count', meansd="Mean (SD)",
                                                 median ='Median', range='Min -
                                                 Max')) #, Nmiss2 ='Missing'

## Setting up descriptives table for study variables
var_table <- tableby(Event ~ 
                       Sex + Race + Age + IQ + FlankerTest +
                       ParentIncome + ParentEducation +  
                       PubertalDevelopment_F + PubertalDevelopment_M + 
                       MatureVideoGames + TotalGamingHours + Weekly_Gaming_Hours +
                       DBD + DBDcu + CU_Traits + Aggression + Externalizing + 
                       Internalizing + Depression + OppositionalDefiant +
                       ConductDisorder,
                     data=df_long, control=descriptives)

# Push variable table object through kable and kable_styling
var_table %>%
  summary(text = TRUE, digits.pct=1, digits=1) %>%
  kable(caption = "Study Descriptives") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, #html_font = "Cambria",
                font_size = 10,
                position = "center", fixed_thead = T) %>%
  row_spec(2:3, extra_css = 'vertical-align: middle !important;') %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(3, border_right = T) %>%
  column_spec(4, border_right = T) %>%
  footnote(general = "TBD. ") %>%
  scroll_box(width = "75%", height = "500px")

```

```{r FEreg}
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

## Longitudinal Fixed Effects Regression
## Load long dataframe
#as_tibble(df_long)

## PubertalDevelopment_F + PubertalDevelopment_M
L_FEreg <-lm(formula = Aggression ~ TotalGamingHours + MatureVideoGames + 
               Sex + Race + Age + IQ + FlankerTest + 
               ParentIncome + ParentEducation + Internalizing, 
             data = df_long)

recall_FEreg_results <- apa_print(L_FEreg, es = "pes")
recall_FEreg_results_p <- apa_print(L_FEreg, es = "pes", in_paren = TRUE)

apa_table(
  recall_FEreg_results_p$table
  , align = c("l", "r", "c", "r", "r", "r")
  , caption = "(Longitudinal Fixed Effects Regression)"
  , note = "(.)"
)

# # ## Linear Mixed Model with a random intercept (LMM-ri)
# #random_intercepts <- lmer(cu_traits ~ 1 + event + vg_total + mature_vg + (1|ids), data = df_long, REML=T)

```

Item valence 
(`r recall_FEreg_results_p$full$TotalGamingHours`) 
and the task affected
`r recall_FEreg_results$full$TotalGamingHours`
xxxxx
(`r recall_FEreg_results_p$full$ParentEducation`) recall performance,
test, 
`r recall_FEreg_results$full$ParentEducation`; the dosage,
however, had no effect on recall.
There was no significant interaction 
(`r recall_FEreg_results_p$full$IQ`).

### Demographic Characteristics
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(1), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

```{r comment=NA, echo = FALSE}
a = 5
b = 6
c = a+b
```

Timmy is `r c` 

```{r output}
#| code-summary: output
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

## Linear Mixed Model with a random intercept (LMM-ri)
#RI <- lmer(Aggression ~ Event + Weekly_Gaming_Hours + (1|ids),
#           data = df_long, REML=T)

## Linear Mixed Model with a random intercept & random slope (LMM-ris)
#RIS <- lmer(Aggression ~ Event + Weekly_Gaming_Hours + 
#              + (1 + Event | ids), data = df_long, REML=T)

## Linear Mixed Model with a random intercept (LMM-ri)
random_intercepts <- lmer(Aggression ~ 1 + Weekly_Gaming_Hours + MatureVideoGames + 
                            Sex + Race + Externalizing +
                            Internalizing + Depression + (1|ids), 
                          data = df_long, REML=T)

summary(random_intercepts)
confint(random_intercepts, level = 0.95, method = "Wald")
random <- estimate_grouplevel(random_intercepts)

#str(df_long$ParentIncomeDel) 
#ParentEducationDel 

```

In text reporting test  
(r random_intercepts$Aggression`) 
In text reporting test 
r rrandom_intercepts`
In text reporting test 
(r random_intercepts$Sex`) recall performance,
In text reporting test 
r random_intercepts$Sex`; the dosage,
In text reporting test 
There was no significant interaction 
r random_intercepts$Depression`).

```{r }
#| code-summary: output
#| include: FALSE
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

# Output and reports extending from the LMM-ri analyses
summary(random_intercepts)
confint(random_intercepts, level = 0.95, method = "Wald")
random <- estimate_grouplevel(random_intercepts)

```

```{r reportz}
#| code-summary: output
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

report(random_intercepts)

```

```{r performance}
#| code-summary: output
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

report_performance(random_intercepts)
```

```{r statistics}
#| code-summary: output
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

report_statistics(random_intercepts)

```

```{r extrct-FE}
#| code-summary: output
#| echo: FALSE
#| warnings: FALSE
#| messages: FALSE

## Obtain LMM-ri model parameters to plot/graph of results
model_intercept <- as.numeric(fixef(random_intercepts)[1])
model_slope <- as.numeric(fixef(random_intercepts)[2])
```

```{r extrct-RE}
#| class.source: 'fold-hide'
#| message: FALSE
#| warning: FALSE
#| echo: FALSE

intercepts <- rep(coef(random_intercepts)$ids[,1], each = 4)
```


```{r meanplot}
#| messages: FALSE
#| warning: FALSE
#| echo: FALSE
#| column: screen-inset-shaded
#| layout-nrow: 2

## Estimated means plot
means <- estimate_means(random_intercepts)
plot(means)

```

```{r barplot}
#| messages: FALSE
#| warning: FALSE
#| echo: FALSE
#| include: FALSE

# Basic ggplot2 barplot with mean
# p<-df_long %>%
#     filter(!is.na(Sex)) %>% # filter on non-missing values  
#     ggplot(aes(x = MatureGames, y = Aggression, fill = Sex)) + #fill = sex
#     geom_col(position = "dodge",
#            stat = "summary",
#            fun = "mean",
#            #fill = "#AA4A44",
#            #color = "#0099f9"
#            ) +
#     #scale_fill_brewer(palette = "Set1") +
#     scale_fill_manual(values = c("#3db5ff", "#0099f9")) +
    #scale_fill_gradient(high = "#B00B69", low = "#0e0e63") +
    #geom_text(aes(label = cu_traits), position = position_dodge(0.9), 
              #vjust = 2, size = 4, color = "#ffffff") +
    # labs(title = "Behavior Problems by Video Game Groups", subtitle = "Simple bar chart",
    #      caption = "Simple caption", x = "Video Game Group", y = "CBCL Aggression") +
    #           #coord_flip() +
    # #geom_hline(yintercept = mean(df$cbcl_agg), linetype = "dashed", size = 1) +
    # theme_minimal() +
    # theme(
    #       plot.title = element_text(color = "#0099f9", size = 20, hjust = 0.5),
    #       plot.subtitle = element_text(face = "bold", hjust = 1),
    #       plot.caption = element_text(face = "italic", hjust = 0),
    #       axis.title.x = element_text(color = "#0099f9", size = 15, face = "bold"),
    #       axis.title.y = element_text(size = 15, face = "italic")
 # )
#p
```

```{r lmmri-graph}
#| echo: FALSE
#| messages: FALSE
#| warning: FALSE
#| label: my-figure
##| fig-asp: 0.61
##| fig-cap: |
##|   This is a caption for my figure, 
##|   using YAML formatting, etc.#| 

#options(tinytex.verbose = TRUE)

#random_intercepts <- lmer(cbcl_agg ~ 1 + event + vg_total+ sex + (1|ids), data = df, #REML=T)

## LMM-ri plot of estimated random intercepts 
model <- lmer(Aggression ~ Sex + (1 | IQ), data = df_long)
preds <- estimate_relation(model, include_random = TRUE)

## Adding fixed effect trajectory to LMM-ri plot 
fixed_pred <- estimate_relation(model) # This time, include_random is FALSE (default)
plot(preds, ribbon = list(alpha = 0)) + # Previous plot
  geom_ribbon(data = fixed_pred, aes(x = Sex, ymin = CI_low, ymax = CI_high), alpha = 0.4) +
  geom_line(data = fixed_pred, aes(x = Sex, y = Predicted), linewidth = 1) 

# Race
# PrntIncome
# PrntEdu
# MatureGames
# Aggression
# Externalizing
# Internalizing
# Depression
# TotalGamingHrs

######
# ggplot(df_long_sub, aes(x = Event, y = Aggression, color=Sex, shape=Sex)) + 
# geom_abline(slope = model_slope, intercept = model_intercept, linetype = "solid", color = "red", linewidth = 1) + 
# geom_point(color = "grey70") + 
# geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
# scale_shape() + 
# geom_segment(aes(x = Event, xend = Event, y = Aggression, yend = fitted(Aggression)), color = "grey70") + 
# scale_y_continuous(expand = c(0, 0), breaks = c(0, 20, 40, 60, 80, 100), limits = c(0, 100)) + 
# scale_x_continuous(expand = c(0, 0), breaks = c(1, 2, 3, 4), limits = c(0, 4)) +
# theme(panel.background = element_blank(),         
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.border = element_rect(colour = "black", fill = NA),
#         legend.position = "none",
#         axis.text = element_text(size = 14), 
#         axis.title = element_text(size = 14)) +
#         labs (x = "Event", y= "Aggression")

#Save the plot
#ggsave("random_intercept.png", units = "in", width = 9, height = 6, dpi = 300)  



```


```{r}
#| echo: FALSE

df_wide<- read_csv("/Users/shawes/Library/CloudStorage/GoogleDrive-swh004@gmail.com/My Drive/Projects/gaming_behav/main/_data/df_wide.csv")

model <-  'i =~ 1*Aggression_T0 + 1*Aggression_T1 + 1*Aggression_T2
          s =~ 0*Aggression_T0 + 1*Aggression_T1 + 2*Aggression_T2
          
# regressions
i ~ Internalizing_T0 + Sex + Age + ParentIncome + ParentEducation + 
MatureVideoGames + Weekly_Gaming_Hours_T0 + MatureVideoGames*Weekly_Gaming_Hours_T0
'
fit <- growth(model, data=df_wide, estimator ="MLR")
summary(fit, standardized = TRUE, fit.measures = TRUE)

```

```{r}

RICLPM <- '
  # Create between components (random intercepts)
  RIx =~ 1*Weekly_Gaming_Hours_T0 + 1*Weekly_Gaming_Hours_T1 + 1*Weekly_Gaming_Hours_T2
  RIy =~ 1*Externalizing_T0 + 1*Externalizing_T1 + 1*Externalizing_T2
  
  # Create within-person centered variables
  wx0 =~ 1*Weekly_Gaming_Hours_T0
  wx1 =~ 1*Weekly_Gaming_Hours_T1
  wx2 =~ 1*Weekly_Gaming_Hours_T2 
  wy0 =~ 1*Externalizing_T0
  wy1 =~ 1*Externalizing_T1
  wy2 =~ 1*Externalizing_T2
  
  # Estimate lagged effects between within-person centered variables
  wx1 + wy1 ~ wx0 + wy0
  wx2 + wy2 ~ wx1 + wy1
  #wy2 ~ wy1
  #wy1 ~ wy0
  
  # Estimate covariance between within-person centered variables at first wave
  wx0 ~~ wy0 # Covariance
  
  # Estimate covariances between residuals of within-person centered variables 
  # (i.e., innovations)
  wx1 ~~ wy1
  wx2 ~~ wy2
  
  # Estimate variance and covariance of random intercepts
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate (residual) variance of within-person centered variables
  wx0 ~~ wx0 # Variances
  wy0 ~~ wy0
  wx1 ~~ wx1 # Residual variances
  wy1 ~~ wy1
  wx2 ~~ wx2
  wy2 ~~ wy2
  
# regressions
#RIy ~ Weekly_Gaming_Hours_T0
#s ~ Weekly_Gaming_Hours_T0 
'

RICLPM.fit <- lavaan(RICLPM, 
  data = df_wide,
  estimator ="MLR",
  #group = "MatureVideoGames",
  #ordered = c("Externalizing_T0", "Externalizing_T1", "Externalizing_T2"),
  meanstructure = T, 
  int.ov.free = T
)

#, ordered = c("Externalizing_T0", "Externalizing_T1", "Externfalizing_T2")

summary(RICLPM.fit, standardized = TRUE, fit.measures = TRUE)
```

### Individual Behavioral Performance Measures
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(1), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

### Structural Equation Modeling
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(1), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

## Discussion
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(4), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

### Limitations
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(1), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

### Conclusions
```{r comment=NA, echo = FALSE}
cat(sapply(
  stri_wrap(stri_rand_lipsum(1), 90, simplify=FALSE),
  stri_flatten, collapse='\n'), sep='\n\n')
```

\newpage

## References
\label{sec:bibliography}




